---
title: Transit-facilitated accessibility of the asentamientos of Greater Buenos Aires,
  Argentina
author: "Kyle Sorlie Titlow"
date: "6/3/2019"
output:
  pdf_document: default
  html_document: default
---

# De Alguna Manera Llegas
## Transit-access to 

```{r setup, include=FALSE}
require(knitr)
knitr::opts_chunk$set(echo = TRUE)
opts_knit$set(root.dir = "~/Documents/Thesis/Data")

#Input libraries
library(rgdal)
library(sf)
library(mapview)

#Set paths to the four geodatabases
gdb_adm0 <- "Data_ADM0_Argentina.gdb/"
gdb_adm1 <- "Data_ADM1_BuenosAiresProvince.gdb/"
gdb_adm2 <- "Data_ADM2_AMBA.gdb/"
gdb_adm3 <- "Data_ADM3_3CaseStudies.gdb/"
gdb_thesis <- "Thesis.gdb/"
output_dsn = "GEOJSON"

```

### 1. Study Area
#### Figure 1.1 -- Republic of Argentina
Map of the Republic of Argentina highlighting the Province of Buenos Aires and the Autonomous City of Buenos Aires
```{r echo=FALSE}
#adm1 <- st_read(dsn=gdb_adm1, layer = "Administrative_Provincias")
#adm1_caba <- st_read(dsn=gdb_adm2, layer = "CABA")
#adm1_prov <- st_read(dsn=gdb_adm1, layer = "Administrative_ProvinceBoundary")
```

#### Figure 1.2: Buenos Aires Province
Showing the relative location of the Autonomous City of Buenos Aires (CABA) and the surrounding conurbation
```{r}
# Import province-wide layers
#st_read(dsn=gdb_adm2, layer = "Departments_GovernmentSeats")
#st_read(dsn=gdb_adm1, layer = "Departments")
```

#### Figure 2.3: Agglomerated Buenos Aires
Map of the departments belonging to Agglomerated Buenos Aires, which encircle CABA 
```{r}
##AGBA with all 30 departments =============================================================================
#adm1_amba30 <- st_read(dsn=gdb_adm2, layer = "AMBACABA_Separate") #2n, 4v
#adm2_amba30 <- st_read(dsn=gdb_adm2, layer = "Departments_AMBACABA_CABA") #47n, 8v
adm2_amba30 <- st_read(dsn=gdb_adm2, layer = "Departments_AGBA30_INDEC") #31n, 28v

##AGBA with 24 departments ================================================================================
#adm1_caba_cbd <- st_read(dsn=gdb_adm2, layer = "AMBACABA_CBD") #1n, 5v
```

#### Figure 2.4: Mancha Urbana
The full extent of Buenos Aires’ agglomerated area, with departmental boundaries superimposed
```{r}
#manchaurbana <- st_read(dsn=gdb_adm2, layer = "UrbanizedArea")

#plot(st_geometry(manchaurbana), axes=T, col="orange")
#plot(st_geometry(adm2_prov), add=T, col=NA, border="light grey")
#plot(st_geometry(adm2_amba), add=T, col=NA, border="dark grey")
#plot(st_geometry(adm0), add=T, col=NA, border="black")
```

#### Figure 2.5: Departments of AGBA
Departments of Agglomerated Buenos Aires (AGBA), based on degree of urbanization and history as part of Greater Buenos Aires (GABA)
```{r}
#plot(st_geometry(adm2_amba), axes=T, col="light grey", border="dark grey")
```

#### Figure 2.6: Population densities
Population density, measured in people per square kilometer, across the departments of Agglomerated Buenos Aires (AGBA)
```{r}
#radio_amba30 <- st_read(dsn=gdb_adm2, layer = "Radio_AGBA30") #13508n, 198v (Excl. SL-Is.)
radio_amba <- st_read(dsn=gdb_adm2, layer = "Radio_AMBA24_INDEC") #13521n, 175v (Incl. SL-Is.) ***

#radio_amba30_indec <- st_read(dsn=gdb_thesis, layer = "Radio_AMBACABA_INDEC") #14433n, 337v (Incl. LP/SL-I/FV)
radio_amba24_indec <- st_read(dsn=gdb_thesis, layer = "Radio_AMBA24_INDEC") #13521n, 172v (Incl. SL-I) ***

#plot(radio_amba["TOT_POB"], border="NA", key.pos=4)
```

#### Figure 2.7: Socioeconomic indicators
Illiteracy rates in Agglomerated Buenos Aires (AGBA), 2010
University-level education rates in agglomerated Buenos Aires (AGBA), 2010
```{r}
plot(layer["PCT_POB_ANALFTABETISMO"], border="NA", key.pos=4)
plot(layer["PCT_POB_NIVELED_UNIV"], border="NA", key.pos=4)
```

### Chapter 3: Transportation
#### Figure 3.1: Transportation infrastructure
Transportation system of Agglomerated Buenos Aires (AGBA)
```{r}
#motorways <- st_read(dsn=gdb_adm2, layer = "RedVial")

#railways <- st_read(dsn=gdb_adm2, layer = "Railroad_AGBA30")
#rail_stations <- st_read(dsn=gdb_adm2, layer = "Railroad_Stations_AGBA30")

#subte <- st_read(dsn=gdb_adm2, layer = "Subway_Route")
#subte_stations <- st_read(dsn=gdb_adm2, layer = "Subway_Stations")

#bus_routes <- st_read(dsn=gdb_adm2, layer = "Bus_AGBA30")
```

#### Figure 3.3: Population density and transportation
Population density (2010) in Agglomerated Buenos Aires (AGBA), overlaid with regional road and railway networks (2018)
```{r}
plot(layer["POB_DENS"], border="NA", key.pos=4)
```

### Chapter 4: Asentamientos
#### Figure 4.2: TECHO asentamientos
Distribution of asentamientos in Agglomerated Buenos Aires (AGBA) (2016)
```{r}
## ADM2: Load asentamiento layers -------------------------------------------------------------
#techo_amba24 <- st_read(dsn=gdb_adm2, layer = "TECHO_AGBA30")                          #1009n, 50v (all types, amba24)

#techo_asent_amba <- st_read(dsn=gdb_adm2, layer = "TECHO_AGBA30_Asentamientos")        #550n, 82v (asent only, amba24)
#asent_amba24_pnt <- st_read(dsn=gdb_thesis, layer = "AMBA24_Asentamientos")            #687n, 126v (asent, amba30, pts)

#techo_villa_amba <- st_read(dsn=gdb_adm2, layer = "TECHO_AMBAINDEC_Villa")             #252n, 50v (villa only, amba30)

#urb_cerradas <- st_read(dsn=gdb_adm2, layer = "UrbanizacionesCerradas_AMBAINDEC")      #100n, 32v (urbcn only, amba30)

#techo_asent_n3 <- st_read(dsn=gdb_adm3, layer = "TECHO_AMBAINDEC_n3")                           #139n, 126v (asent only, n3)
```

#### Figure 4.3: Asentamientos and transportation
The asentamientos of Agglomerated Buenos Aires (AGBA), overlaid with major regional transportation infrastructure (2018)

### Chapter 6: Methodology
#### Figure 6.1: Census geography
Map of all census geographic units in Agglomerated Buenos Aires (AGBA), including provinces, departments, fractions, and radios (2010)
```{r}
#layer <- st_read(dsn=gdb_adm2, layer = "Radio_AGBA30")
```

#### Figure 6.3: Census geography and asentamientos
Map of census radios in Agglomerated Buenos Aires, colored based percent overlap with an asentamiento (2013)
```{r}
#layer <- st_read(dsn=gdb_adm2, layer = "Radio_AGBA30")
```


#### Figure 6.4: Asentamientos, by department
Departments of Agglomerated Buenos Aires (AGBA), by number of families estimated to be living in asentamientos (2013)
```{r}
#adm2_amba30_ext <- st_read(dsn=gdb_adm3, layer = "Departments_AMBA30")        #31n, 28v
#adm2_amba30_ext <- st_transform(adm2_amba30_ext, 4326)
#adm2_amba30 <- st_read(dsn=gdb_adm3, layer = "Departments_AMBA24")            #31n, 24v
#adm2_amba30 <- st_transform(adm2_amba30, 4326)

#plot(st_geometry(adm2_amba30_ext), axes=T, col="grey")
#plot(st_geometry(adm2_amba30), add=T, col="light blue")
```


#### Figure 6.5: Case studies
Departments of Agglomerated Buenos Aires (AGBA), highlighting the three selected as case studies: La Matanza, Pilar, and Quilmes
```{r}
#adm2_n3 <- st_read(dsn=gdb_adm3, layer = "Departments_AMBAINDEC_n3")        #n3, v5
#adm2_n3 <- st_transform(adm2_n3, 4326)

#radio_amba <- st_read(dsn=gdb_adm3, layer = "Radio_AMBA24_INDEC_Pct_n3")   #2138n, 171v
#radio_amba <- st_read(dsn=gdb_adm3, layer = "Radio_AMBAINDEC_n3")          #2138n, 175v
```

#### Figure 6.6: Quilmes
Locations of asentamientos and transportation infrastructure, Quilmes department
Sampled census radios (by degree of overlap with asentamiento), Quilmes department
```{r}
#asent_qlm <- st_read(dsn=gdb_thesis, layer = "Quilmes_Asentamientos") #43n, 82v (poly)
#orig_qlm_trvtime <- st_read(dsn=gdb_thesis, layer = "Quilmes_Origins_Radios_12March") #92n x 35v (pts)
```

#### Figure 6.7: La Matanza
Locations of asentamientos and transportation infrastructure, La Matanza department
Sampled census radios (by degree of overlap with asentamiento), La Matanza department
```{r}
#asent_lmz <- st_read(dsn=gdb_thesis, layer = "LaMatanza_Asentamientos") #69n, 82v (poly)
#orig_lmz_trvtime <- st_read(dsn=gdb_thesis, layer = "LaMatanza_Origins_Radios_12March") #120n, 33v (point)
```


#### Figure 6.8: Pilar Asentamientos, Transportation, and Sampled Radios
Locations of asentamientos and transportation infrastructure, Pilar department
Sampled census radios (by degree of overlap with asentamiento, Pilar department
```{r}
#asent_plr <- st_read(dsn=gdb_thesis, layer = "Pilar_Asentamientos") #30n, 82v
#orig_plr_trvtime <- st_read(dsn=gdb_thesis, layer = "Pilar_Origins_Radios_12March") #72n, 33v (point)
```


#### Figure 6.9: Departments with population estimates
Departments of Agglomerated Buenos Aires (AGBA), overlaid with SEDAC population estimates (2015)
```{r}
```

#### Figure 6.10: Weighted Population Centers of Sampled Census Radios
Weighted mean population centers of sampled census radios, by overlap with an asentamiento (2013) and from all three case studies
```{r}
## ADM3: Load origin layers: ------------------------------------------------------------------
#st_read(dsn=gdb_adm3, layer = "Study3_Origins_Radios_MeanCenter_All")          #284n, 28v
#st_read(dsn=gdb_adm3, layer = "Origins_Radios_All_PopMeanCenter")              #284n, 21v
#st_read(dsn=gdb_adm3, layer = "Origins_Radios_PopMeanCenter_INDEC")            #284n, 174v
#st_read(dsn=gdb_adm3, layer = "Study3_Origins_Radios_MeanCenter_withINDEC")    #284n, 213v
#st_read(dsn=gdb_adm3, layer = "Study3_Origins_MAJ")                            #52n, 209v
#st_read(dsn=gdb_adm3, layer = "Study3_Origins_MIN")                            #90, 209v
#st_read(dsn=gdb_adm3, layer = "Study3_Origins_NONE")                           #142n, 209v
#st_read(dsn=gdb_adm3, layer = "Study3_Origins_ANY")                            #142n, 209v
#st_read(dsn=gdb_adm3, layer = "thesis_traveltime_3cases_indec_scaled")         #284n, 207v
#st_read(dsn=gdb_thesis, layer = "Study3_Origins_Radios_MeanCenter_withINDEC")  #284n, 179v
#st_read(dsn=gdb_thesis, layer = "AGBA30_Origins")                              #284n, 211v
#st_read(dsn=gdb_thesis, layer = "Study3_Origins_Radios_MeanCenter_All")        #284, 31v
```

#### Figure 6.11: Central Business Districts
Central business districts of Agglomerated Buenos Aires (AGBA), featuring those included as “destinations” for the corresponding API requests
```{r}
#st_read(dsn=gdb_adm3, layer = "CBD_BuenosAires")                                       #1n, 5v
#st_read(dsn=gdb_adm3, layer = "CBD_Proximate")                                         #21n, 29v
#st_read(dsn=gdb_adm3, layer = "Departments_AMBAINDEC_BorderSample")                    #23n, 8v (error)

#st_read(dsn=gdb_adm3, layer = "CBD_Pilar")                                             #1n, #7v
#st_read(dsn=gdb_adm3, layer = "CBD_Quilmes")                                           #1n, #7v
#st_read(dsn=gdb_adm3, layer = "CBD_LaMatanza")                                         #1n, #7v
```

#### Figure 6.12: Railroad Stations
Railroad stations of Agglomerated Buenos Aires (AGBA), featuring those included as “destinations” for the corresponding API requests

#### Figure 6.13: Public Schools
Public kindergartens (left), primary schools (center), and secondary schools (right) of Agglomerated Buenos Aires (AGBA), featuring those included as “destinations” for the corresponding API requests
```{r}
```

#### Figure 6.14: Public Healthcare
UPA’s (left), public hospitals (center), and public diagonstic/treatment centers (right) of Agglomerated Buenos Aires (AGBA), featuring those included as “destinations” for the corresponding API requests
```{r}
```


### Map Appendix
#### Figure A.1
Travel times on public transportation (at 7:00am on a Wednesday) from all sampled census radios to the central business district of the Autonomous City of Buenos Aires (CABA)

#### Figure A.2
Travel times on public transportation (at 7:00am on a Wednesday) from all sampled census radios to the central business districts of their respective departments

#### Figure A.3
Travel times on public transportation (at 7:00am on a Wednesday) from all sampled census radios to the nearest central business district of any department

#### Figure A.4
Travel times on public transportation (at 7:00am on a Wednesday) from all sampled census radios to the nearest railway station

#### Figure A.5
Travel times on public transportation (at 10:30am on a Wednesday) from all sampled census radios to the nearest urgent care center (UPA)

#### Figure A.6
Travel times on public transportation (at 10:30am on a Wednesday) from all sampled census radios to the nearest public hospital

#### Figure A.7
Travel times on public transportation (at 10:30am on a Wednesday) from all sampled census radios to the nearest public diagnostic/treatment center

#### Figure A.8
Travel times on public transportation (at 12:00pm on a Wednesday) from all sampled census radios to the nearest public kindergarten

#### Figure A.9
Travel times on public transportation (at 12:00pm on a Wednesday) from all sampled census radios to the nearest public primary school

#### Figure A.10
Travel times on public transportation (at 12:00pm on a Wednesday) from all sampled census radios to the nearest public secondary school



